---
title: "traits.CWM.plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(cowplot)
library(viridis)
library(broom)
library(ggplot2)
library(lubridate)
library(lme4)
#library(ggeffects)
library(sjPlot)
```


```{r}
#weighted.traits made from 01a. with df.cover.long2 from load and format.
weighted.traits.cwm <- weighted.traits.plot
#weighted.traits.cwm$phyD <-  data.frame(phyD = substr(weighted.traits.cwm$Code,1,1)) 
#unlist(weighted.traits.cwm$phyD) -> weighted.traits.cwm$phyD
#weighted.traits.cwm$fd <-  data.frame(fd = substr(weighted.traits.cwm$Code,2,2)) 
#unlist(weighted.traits.cwm$fd) -> weighted.traits.cwm$fd
cwm <- reshape2::melt(weighted.traits.cwm,  id.vars = c("year", "plot", "type", "phyD", "fd"), variable.name = "Traits") 
cwm$fd <- as.factor(cwm$fd)
cwm <- split(cwm, cwm$Traits)
sm <- aov(value ~ type:fd, data=cwm$seedMass) 
TukeyHSD(sm)

#Add letters for significance:
generate_label_df <- function(TUKEY, variable){
  # Extract labels and factor levels from Tukey post-hoc 
  Tukey.levels <- variable[,4]
  Tukey.labels <- data.frame(multcompLetters(Tukey.levels)['Letters'])
  #I need to put the labels in the same order as in the boxplot :
  Tukey.labels$treatment=rownames(Tukey.labels)
  Tukey.labels=Tukey.labels[order(Tukey.labels$treatment) , ]
  return(Tukey.labels)
}

TRAIT <- "SLA"
for (facetk in as.character(unique(cwm$vegetativeHeight$fd))) {   
  subdf <- subset(cwm$vegetativeHeight, fd==facetk)
  model=lm(value ~ type:fd, data=cwm$vegetativeHeight)
  ANOVA=aov(model)
  TUKEY <- TukeyHSD(ANOVA)#
  labels <- generate_label_df(TUKEY , TUKEY$`type:fd`)
}

sm <- MCMCglmm(seedMass ~ type + type:fd, random = ~plot, data=weighted.traits.cwm, nitt = 100000, thin=100, burnin=10000)
cwm.lmer.model <- lmer(value ~ type + type*fd + (1|plot), data=cwm)

as.numeric(weighted.traits.cwm$year) -> weighted.traits.cwm$year
cwm.mler <- lmer(vegetativeHeight ~ year + fd + phyD + (1|plot), data=weighted.traits.cwm)
vh <- plot_model(cwm.mler, type = "pred", terms = "year")

lmer.sla <- lmer(SLA ~ year + fd + phyD + (1|plot), data=weighted.traits.cwm)
sla <- plot_model(lmer.sla, type = "pred", terms = "year")

lmer.sdmc <- lmer(SDMC ~ year + fd + phyD + (1|plot), data=weighted.traits.cwm)
sdmc <- plot_model(lmer.sdmc, type = "pred", terms = "year")
 
lmer.lnc <- lmer(LNC ~ year + fd + phyD + (1|plot), data=weighted.traits.cwm)
lnc <- plot_model(lmer.lnc, type = "pred", terms = "year")
 
plot_grid(vh, sla, sdmc, lnc) -> predicted.cwms
```

#CWMs traits by year
```{r}
df.cover.na.glm.long.trait$Plug -> datCov.long.trait
names(datCov.long.trait)[names(datCov.long.trait) == 'value'] <- 'cover'

a <- ggplot(datCov.long.trait, aes(x=SDMC, y=cover, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method=lm) +
  scale_color_brewer(palette="Blues") +
  labs(x="stem dry matter content (SDMC)", y="abs. cover")

rownames(CovChange) -> CovChange$Species
newdf <- merge(datCov.long.trait, CovChange, by="Species")
names(newdf)[names(newdf) == 'yr2-yr3'] <- 'deltaCover2'
names(newdf)[names(newdf) == 'yr1-yr2'] <- 'deltaCover1'

aa <- ggplot(newdf, aes(x=SDMC, y=deltaCover2)) +
  geom_point(aes(color=type, shape=type)) + 
  geom_smooth(method="lm", aes(color=type)) +
  scale_color_brewer(palette="Reds") +
  labs(x="stem dry matter content (SDMC)", y="delta cover")

b <- ggplot(datCov.long.trait, aes(x=LDMC, y=cover, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method="lm", formula = y ~ x + I(x^2)) +
  scale_color_brewer(palette="Greens") +
  labs(x="leaf dry matter content (LDMC)", y="abs. cover")

bb <- ggplot(newdf, aes(x=LDMC, y=deltaCover2, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method=lm) +
  scale_color_brewer(palette="Blues") +
  labs(x="leaf dry matter content (LDMC)", y="delta cover")

c <- ggplot(datCov.long.trait, aes(x=seedMass, y=cover, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method=lm) +
  scale_color_brewer(palette="Reds") +
  labs(x="seed mass", y="abs. cover")

cc <- ggplot(newdf, aes(x=seedMass, y=deltaCover2, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method=lm) +
  scale_color_brewer(palette="Reds") +
  labs(x="seed mass", y="delta cover")

d <-ggplot(datCov.long.trait, aes(x=vegetativeHeight, y=cover, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method="lm", formula = y ~ x + I(x^2)) +
  scale_color_brewer(palette="Oranges") +
  labs(x="vegetative height", y="abs. cover")

dd <-ggplot(newdf, aes(x=vegetativeHeight, y=deltaCover2, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method="auto") +
  scale_color_brewer(palette="Oranges") +
  labs(x="vegetative height", y="delta cover")


e <- ggplot(datCov.long.trait, aes(x=cover, y=LNC, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method=lm) +
  scale_color_brewer(palette="Purples")

f <- ggplot(datCov.long.trait, aes(x=cover, y=SLA, color=type, shape=type)) +
  geom_point() + 
  geom_smooth(method=lm) +
  scale_color_brewer(palette="Greys")

traits.by.cover <- plot_grid(a, c, d, b, labels = "AUTO", nrow = 2)
ggsave(traits.by.cover, file="../OUT/traits~cover.png")
```

```{r}
# get mean and SDs of CWMs from weighted.traits
stderror <- function(x) sd(x)/sqrt(length(x)) # standard error function
CWMs <- weighted.traits %>%
  group_by(year, type)  %>%
  summarise_at(.vars = vars(seedMass,LDMC,SLA, SDMC, vegetativeHeight, LNC, LCC),
               .funs = c(Mean="mean", Sd="sd", SE = "stderror") )

mm <- reshape2::melt(CWMs, id.var=c("year", "type"))
trait_names <- c(
  'seedMass_Mean'="seed M",
  'LDMC_Mean'="LDMC",
  'SLA_Mean'="SLA",
  'SDMC_Mean'="SDMC", 
  'vegetativeHeight_Mean' = "Veg.Ht", 
  'LNC_Mean' = "LNC",
  'LCC_Mean'= "LCC", 
  'flowerHeight_Mean'="Flwr.Ht"
)
theme_set(theme_bw())
library("ggsci")

f <- ggplot(mm[1:80,], aes(x = year, y = value, group = type)) + geom_line(aes(color = variable, linetype=type)) +
      facet_grid(variable ~ ., scales = "free", labeller = as_labeller(trait_names)) 
cwm.plot <- f + labs(x="year", y="CWM") + theme_bw() +
   theme(strip.background = element_rect(colour="grey", fill="white", 
                                       size=1.5, linetype="solid")) +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
scale_colour_manual(values = pal_jco()(8))
 
##
cwm.long <- reshape2::melt(weighted.traits.plot, id.var=c("year", "type", "phyD", "plot", "fd"), value.name="value", variable.name="trait")

cwm.long.sd <- cwm.long %>%
  group_by(year, type, phyD, trait)  %>%
  summarise_at(.vars = vars(value),
               .funs = c(Mean="mean", Sd="sd", SE = "stderror") )

split(cwm.long.sd, cwm.long.sd$type) -> mm.mice.phyd
test <- filter(mm.mice.phyd$Plug, trait %in% c("seedMass", "LDMC", "LCC", "vegetativeHeight", "SDMC", "LNC", "leafLength"))

as.data.frame(test) -> test
as.character(test$trait) -> test$trait

f.mice2 <- ggplot(test, aes(x = year, y = Mean, group = phyD)) + geom_line(aes(color=trait, linetype=phyD)) +
      facet_grid(trait ~ ., scales = "free") 
cwm.mice.plot <- f.mice2 + labs(x="year", y="CWM") + theme_bw() +
   theme(strip.background = element_rect(colour="grey", fill="white", 
                                       size=1.5, linetype="solid")) +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
scale_colour_manual(values = pal_jco()(8)) + geom_errorbar(aes(ymin=Mean-Sd, ymax=Mean+Sd)) +         facet_grid(trait ~ ., scales = "free") 

#now add SD:
split(test, test$trait) -> test.trt
ggplot(test.trt$SDMC, aes(x = year, y = Mean, group = phyD)) + geom_line(aes(color=phyD, linetype=phyD)) +
      facet_grid(phyD ~ ., scales = "free") + geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE)) +         facet_grid(phyD ~ ., scales = "free") 

